---
title: "Homework 5"
output: github_document
author: Sushupta Vijapur (smv2138)
---
```{r}
library(tidyverse)
library(rvest)
library(httr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

## all plots i make will have the viridis color palette
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

```

## Problem 1

```{r}
homicide_df = 
  read_csv("hom_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved"
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```

Let's look at this a bit

```{r}
aggregate_df = 
    homicide_df %>% 
      group_by(city_state) %>% 
      summarize(
        hom_total = n(),
        hom_unsolved = sum(resolved == "unsolved")
      )
```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved),
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```


Try to iterate
map2 gives you 2 inputs (hom unsolved and hom total)
```{r}
results_df = 
  aggregate_df %>% 
    mutate(
      prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
      tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
    ) %>% 
    select(-prop_tests) %>% 
    unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

Created a point estimate for the unsolved homicides by city state in the US

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```


```{r}

homicide_df = 
  read_csv("hom_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved"
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```


## Problem 2

How do you do read csv across all 20 paths?
Ideally you want all 20 csvs stored with the path next to it
```{r}
path_df = 
  tibble(
  path = list.files("long_data")
  ) %>% 
  mutate(path = str_c("long_data/", path),
         path_expand = map(.x = path, ~read_csv(.x))
  ) %>% 
  unnest(path_expand) %>% 
  mutate(
    arm = if_else(str_detect(path, "con"), "control", "exp")
  )
  
         


read_csv(path_df$path[[1]])
```


## Problem 3

don't export mean and sd - export t test results for whether the mean is equal to 0 (p-value and estimate are exported) (always testing the null hypothesis that the mean is equal to 0)

plot estimate mean by true mean (filter for only results where p <0.05, then compute the mean )






