---
title: "Homework 5"
output: github_document
author: Sushupta Vijapur (smv2138)
---
```{r}
library(tidyverse)
library(rvest)
library(httr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

## all plots i make will have the viridis color palette
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

```

## Problem 1

```{r}
homicide_df = 
  read_csv("hom_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved"
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```

Let's look at this a bit

```{r}
aggregate_df = 
    homicide_df %>% 
      group_by(city_state) %>% 
      summarize(
        hom_total = n(),
        hom_unsolved = sum(resolved == "unsolved")
      )
```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved),
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```


Try to iterate
map2 gives you 2 inputs (hom unsolved and hom total)
```{r}
results_df = 
  aggregate_df %>% 
    mutate(
      prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
      tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
    ) %>% 
    select(-prop_tests) %>% 
    unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

Created a point estimate for the unsolved homicides by city state in the US

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```


```{r}

homicide_df = 
  read_csv("hom_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved"
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```


## Problem 2

Start with a dataframe containing all file names; the list.files function will help
Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
```{r}
path_df = 
  tibble(
  path = list.files("long_data")
  ) %>% 
  mutate(path = str_c("long_data/", path),
         path_expand = map(.x = path, ~read_csv(.x))
  ) %>% 
  unnest(path_expand) %>% 
  mutate(
    id_arm = str_sub(path, -10, -5)
    ) %>% 
  relocate(id_arm)
 
         
```


Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.
```{r}
path_df %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "measurements"
  ) %>% 
  ggplot(aes(x = week, y = measurements, group = id_arm)) +
  geom_line(aes(color = id_arm))
```


## Problem 3

don't export mean and sd - export t test results for whether the mean is equal to 0 (p-value and estimate are exported) (always testing the null hypothesis that the mean is equal to 0)

plot estimate mean by true mean (filter for only results where p <0.05, then compute the mean )


```{r}
sim = function(samp_size = 30, mu = 0, sigma = 5) {
  
  sim_data = 
    tibble(
    x = rnorm(n = samp_size, mean = mu, sd = sigma)
  )
  
  sim_data %>% 
    summarize(
      mean = mean(x),
      sd = sd(x)
    )
}

output = vector("list", length = 5000)

for (i in 1:5000) {
  
  output[[i]] = sim(samp_size = 30)
  
}


output_final = bind_rows(output)
```

```{r}
results_mean_sd = 
  output_final %>% 
  mutate(
    results_mean_sd = map(output, t.test)
  )
  

t.test(output[[1]])

results_mean_sd = map(output, t.test)


```




